### 2024-02-06 doc/15yrsChange.Rmd
New Section Headings and Initial Drafts of Paragraphs

# Abstract  {-#Abstract}

@@

*(describe location, forest type, etc)*

@@

@@

@@

@@

# Conclusions (optional)

@@

# Conflict of Interest statement {-#Conflict}
The authors declare no conflict of interest.

# Authors' contributions {-#Authors}
*[Name of author 1] and [Name of author 2] conceived the ideas and designed methodology; [Name of author 1] and [Name of author 3] collected the data; [Name of author 2] and [Name of author 4] analysed the data; [Name of author 1] and [Name of author 4] led the writing of the manuscript. All authors contributed critically to the drafts and gave final approval for publication.*

@@

>>>>

*(Word limit: 6,500 words)*

# Summary  {-#Abstract}

*Summary formats tend to be in a few long bullet points

@@

The study was conducted at The Smithsonian Conservation Biology Institute’s (SCBI) large forest dynamics plot in Front Royal, Virginia, USA (38.8935°, -78.1454°; Bourg et al. 2013, Anderson-Teixeira et al. 2015). *A sentence about the region and that it is adjacent to the northern entrance of Shenandoah National Park.* The plot is 25.6 ha (640 x 400 m) and includes a 4-ha, 2.4 m high deer exclusion fence, which has decreased the number/decreased the presence of white-tailed deer since 1990 (McShea 2000). It consists of a mature secondary eastern deciduous forest that developed following logging and agricultural use in the mid-19th century. The species composition reflects what is typical of this forest type, with a canopy that is dominated by tulip poplar (*Liriodendron tulipifera*), oak (*Quercus spp.*), and hickory (*Carya spp.*), and the understory that is primarily composed of spicebush (*Lindera benzoin*), paw-paw (*Asimina triloba*), American hornbeam (*Carpinus caroliniana*), and witch hazel (*Hamamelis virginiana*)

*Which definition of forest type is more accurate - mature, mixed deciduous forest or mature secondary eastern deciduous forest?*

*Need to add the Anderson-Teixeira et al. 2015 reference to references page*

@@

Data was collected according to the standard ForestGEO protocol, outlined in (Condit 1998). A census crew measured the diameter at breast height (DBH), mapped, and tagged every stem on the plot with a DBH greater than or equal to 1 cm. DBH was recorded only for living trees. If there were multiple stems on a tree, each stem was measured and given a stem number and tag.

@@

In addition to the ForestGEO census, an annual [official name of mortality survey] is conducted on the large forest dynamics plot. The survey assesses the health of individual trees and identifies factors that contribute to mortality. The survey was initiated in 2008, and has been conducted every year since 2013. (source). The field crew measured the percentage of the crown that was alive and intact, and noted any factors associated with death (i.e. wounds) present on the tree.  Numerous nuisance species and pathogens, including the emerald ash borer, white-tailed deer, and dutch elm disease have been recorded in the region prior to the start of the mortality survey (Herms & McCullough, 2014, McShea 2000,NEED ELM SOURCE).

@@

*(describe QA/QC and technical workflow)*

Field data was collected on Apple iPads using the ESRI ArcGIS Field Maps application. To improve the quality of the data, GitHub Actions continuous integration was implemented for quality control (Kim et al., 2022). Data from the previous census was used to populate the Field Maps app, and fields were created to input data. There were checks built into the app to help catch errors, for example the DBH field would flag a suspiciously high number and would not allow the form to be submitted if it was blank. To use the app in the field the census crew downloaded offline areas of where they were working and synced them to an online map after collecting data. Next the data was downloaded from ArcGIS online and pushed to GitHub, where it triggered a GitHub Action running data quality assurance and control (QA/QC) scripts. The scripts were written in R and checked the data for errors such as “suspicious positive growth.” After going through the QA/QC process, a csv of errors and warnings with the associated stem were output which could then be corrected in the field.

@@

# Conclusions (optional) *(No Conclusions section listed in Submission Guidelines)*

@@

# Competing Interests {-#Conflict}
The authors declare no conflict of interest.

# Author Contributions {-#Authors}
*[Name of author 1] and [Name of author 2] conceived the ideas and designed methodology; [Name of author 1] and [Name of author 3] collected the data; [Name of author 2] and [Name of author 4] analysed the data; [Name of author 1] and [Name of author 4] led the writing of the manuscript. All authors contributed critically to the drafts and gave final approval for publication.*

@@

# Supporting Information
